Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-25 cordillera-cycle.tex
Rev. Marshall: rework SIA+SSA limits statement.

      Ice sheet dynamics are typically modelled using a~combination of
      internal deformation and basal sliding. PISM is a~shallow ice sheet
      model, which implies that the balance of stresses is approximated
      based on their predominant components. The Shallow Shelf Approximation
      (SSA) is combined with the Shallow Ice Approximation
      (SIA) by adding velocity solutions of the two approximations
      \citep[Eqs.~7--9 and 15]{Winkelmann.etal.2011}. The computational
      efficiency of this hybrid scheme nevertheless comes at the cost of
      violating stress conservation in the transition zone where
      gravitational stresses have a~double contribution to computed SIA and
      SSA velocities, leading to a~positive bias of total ice velocity that
      remains to be quantified.

>>>>

      Ice sheet dynamics are typically modelled using a~combination of
      internal deformation and basal sliding. PISM is a~shallow ice sheet
      model, which implies that the balance of stresses is approximated
      based on their predominant components. The Shallow Shelf Approximation
      (SSA) is combined with the Shallow Ice Approximation
      (SIA) by adding velocity solutions of the two approximations
      \citep[Eqs.~7--9 and 15]{Winkelmann.etal.2011}. Although this
      heuristic imply errors in the transition zone where gravitational
      stresses intervene both in the SIA and SSA velocity computation, this
      hybrid scheme is computationally much more efficient than a fully
      three-dimensional model with which the simulations presented here
      would not be feasible.
